---
title: "Demo for Starbucks in NY States by Counties"
author: "Nikky Xiong"
date: "3/5/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is a demo EDA for the number of Starbucks in the New York State and the demographics of surrounding neighborhood by counties. Data from https://www.kaggle.com/harrisothman/starbucks-stores-and-new-york-county-demographics.

```{r}
library(readr)
df <- read.csv('raw_data/num_starbucks_nyc.csv')
```

## Overview of the Dataset

```{r, message=FALSE, warning=FALSE}
library(dplyr)
df %>% summary()
```

## Sorted by Number of Starbucks Stores in the New York State

```{r}
dv <- df %>% arrange(desc(NbShops)) %>% 
  select(County, NbShops) %>% 
  filter(NbShops != 0)
dv
```

## Scatter plots to view the relationship between the number of stores and the demographic factors in the county

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(ggthemes)
library(ggrepel)

# Number of Starbucks stores vs Population
pc1 <- ggplot(df, aes(x = Population, y = NbShops)) + 
    geom_point(color = '#87dc97') +
    xlab('Population') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Data Source: Kaggle') +
    geom_smooth(method=lm, se=FALSE, 
                color="#ABA9A9", linetype="dashed") +
    ggtitle('Starbucks Number vs Local Population') +
    theme_linedraw() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8)) 
pc1

# Number of Starbucks stores vs Density of Population
pc2 <- ggplot(df, aes(x = DensityOfPopulation, y = NbShops)) + 
    geom_point(color = '#87dc97') +
    xlab('Density of Population') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Data Source: Kaggle') +
    geom_smooth(method=lm, se=FALSE, 
                color="#ABA9A9", linetype="dashed") +
    ggtitle('Starbucks Number vs Local Population Density') +
    theme_linedraw() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5))
pc2

# Number of Starbucks stores vs Average Income
pc3 <- ggplot(df, aes(x = AverageIncome, y = NbShops)) + 
    geom_point(color = '#87dc97') +
    xlab('Average Income') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Data Source: Kaggle') +
    geom_smooth(method=lm, se=FALSE, 
                color="#ABA9A9", linetype="dashed") +
    ggtitle('Starbucks Number vs Local Average Income') +
    theme_linedraw() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8))
pc3

# Number of Starbucks stores vs Median Age
pc4 <- ggplot(df, aes(x = MedianAge, y = NbShops)) + 
    geom_point(color = '#87dc97') +
    xlab('Median Age') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Data Source: Kaggle') +
    geom_smooth(method=lm, se=FALSE, 
                color="#ABA9A9", linetype="dashed") +
    ggtitle('Starbucks Number vs Local Median Age') +
    theme_linedraw() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8))
pc4

# Number of Starbucks stores vs Density of Shops
pc5 <- ggplot(df, aes(x = DensityOfShops, y = NbShops)) + 
    geom_point(color = '#87dc97') +
    xlab('Density of Shops') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Data Source: Kaggle') +
    geom_smooth(method=lm, se=FALSE, 
                color="#ABA9A9", linetype="dashed") +
    ggtitle('Starbucks Number vs Local Shop Density') +
    theme_linedraw() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8))
pc5
```

## Linear regression to investigate the relationship between

```{r}
library(jtools)
lm <- lm(NbShops ~ Population + DensityOfPopulation +
             AverageIncome + MedianAge + DensityOfShops, data = df)
summary(lm)
summ(lm)
```


```{r}
lm2 <- lm(NbShops ~ Population, data = df)
summary(lm2)
summ(lm2)
```

```{r}
lm3 <- lm(NbShops ~ DensityOfPopulation, data = df)
summary(lm3)
summ(lm3)
```

```{r}
lm4 <- lm(NbShops ~ AverageIncome, data = df)
summary(lm4)
summ(lm4)
```

```{r}
lm5 <- lm(NbShops ~ MedianAge, data = df)
summary(lm5)
summ(lm5)
```

## To predict the number of Starbucks stores 

### GLM

```{r, warning=FALSE, message=FALSE}
library(caret)

ctrl <- trainControl(method = "cv", number = 10)
set.seed(12345)
in_training <- createDataPartition(y = df$NbShops, 
                                   p = 0.8, list = FALSE)
training <- df[in_training, ]
testing <- df[-in_training, ]
Grid <- expand.grid(.lambda = seq(.05, 1, length = 10),
                    .alpha = seq(.05, 1, length = 10))
```

```{r}
ols1 <- lm(NbShops ~ Population + DensityOfPopulation +
             AverageIncome + MedianAge + DensityOfShops, 
           data = training)
ols2 <- lm(NbShops ~ DensityOfPopulation + Population + AverageIncome, data = training)
ols3 <- lm(NbShops ~ DensityOfPopulation + Population, 
           data = training)
```

```{r}
mod1 <- train(formula(ols1), data = training, method = "glmnet", 
               trControl = ctrl, tuneGrid = Grid)
y_hat_mod1 <- predict(mod1, newdata = testing)
defaultSummary(data.frame(obs = testing$NbShops, 
                          pred = y_hat_mod1))
```

```{r}
mod2 <- train(formula(ols2), data = training, method = "glmnet", 
               trControl = ctrl, tuneGrid = Grid)
y_hat_mod2 <- predict(mod2, newdata = testing)
defaultSummary(data.frame(obs = testing$NbShops, 
                          pred = y_hat_mod1))
```

```{r}
mod3 <- train(formula(ols3), data = training, method = "glmnet", 
               trControl = ctrl, tuneGrid = Grid)
y_hat_mod3 <- predict(mod3, newdata = testing)
defaultSummary(data.frame(obs = testing$NbShops, 
                          pred = y_hat_mod1))
```