---
title: "Demo for Starbucks in NY States by Counties"
author: "Nikky Xiong"
date: "3/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is a demo EDA for the number of Starbucks in the New York State and the demographics of surrounding neighborhood by counties. Data from https://www.kaggle.com/harrisothman/starbucks-stores-and-new-york-county-demographics.

```{r}
library(readr)
df <- read.csv('raw_data/num_starbucks_nyc.csv')
```

## Overview of the Dataset

```{r, message=FALSE, warning=FALSE}
library(dplyr)
df %>% summary()
```

## Sorted by Number of Starbucks Stores in the New York State

```{r}
df %>% arrange(desc(NbShops))
```

## Scatter plots to view the relationship between the number of stores and the demographic factors in the county

```{r}
library(ggplot2)
library(ggthemes)
library(ggrepel)

# Number of Starbucks stores vs Population
pc1 <- ggplot(df, aes(x = Population, y = NbShops)) + 
    geom_point() +
    xlab('Population') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Kaggle') +
    ggtitle('Starbucks Number vs Local Population') +
    theme_fivethirtyeight() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8)) 
pc1

# Number of Starbucks stores vs Density of Population
pc2 <- ggplot(df, aes(x = DensityOfPopulation, y = NbShops)) + 
    geom_point() +
    xlab('Density of Population') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Kaggle') +
    ggtitle('Starbucks Number vs Local Population Density') +
    theme_fivethirtyeight() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5))
pc2

# Number of Starbucks stores vs Average Income
pc3 <- ggplot(df, aes(x = AverageIncome, y = NbShops)) + 
    geom_point() +
    xlab('Average Income') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Kaggle') +
    ggtitle('Starbucks Number vs Local Average Income') +
    theme_fivethirtyeight() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8))
pc3

# Number of Starbucks stores vs Median Age
pc4 <- ggplot(df, aes(x = MedianAge, y = NbShops)) + 
    geom_point() +
    xlab('Median Age') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Kaggle') +
    ggtitle('Starbucks Number vs Local Median Age') +
    theme_fivethirtyeight() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8))
pc4

# Number of Starbucks stores vs Density of Shops
pc5 <- ggplot(df, aes(x = DensityOfShops, y = NbShops)) + 
    geom_point() +
    xlab('Density of Shops') + 
    ylab('Number of Starbucks Stores in the County') + 
    labs(caption = 'Kaggle') +
    ggtitle('Starbucks Number vs Local Shop Density') +
    theme_fivethirtyeight() +
    theme(plot.title = element_text(size=14, face="bold", hjust = 0.5),
          legend.text = element_text(size=8),
          legend.title = element_text(size=8))
pc5
```

## Linear regression to investigate the relationship between 

```{r}
lm <- lm(NbShops ~ Population + DensityOfPopulation +
             AverageIncome + MedianAge + DensityOfShops, data = df)
summary(lm)
```


## Machine Learning models to predict the number of Starbucks stores by the unsupervised learning method (GLM)

```{r, warning=FALSE, message=FALSE}
library(caret)

ctrl <- trainControl(method = "cv", number = 10)
set.seed(12345)
in_training <- createDataPartition(y = df$NbShops, 
                                   p = 0.8, list = FALSE)
training <- df[in_training, ]
testing <- df[-in_training, ]
Grid <- expand.grid(.lambda = seq(.05, 1, length = 10),
                    .alpha = seq(.05, 1, length = 10))
```

```{r}
ols1 <- lm(NbShops ~ Population + DensityOfPopulation +
             AverageIncome + MedianAge + DensityOfShops, 
           data = training)
```

```{r}
mod1 <- train(formula(ols1), data = training, method = "glmnet", 
               trControl = ctrl, tuneGrid = Grid)
y_hat_mod1 <- predict(mod1, newdata = testing)
defaultSummary(data.frame(obs = testing$NbShops, 
                          pred = y_hat_mod1))
```

