---
title: "NYC Zip Demographics"
author: "Nikky Xiong"
date: "3/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

source: Department of Health, New York State (2006/03)
https://www.health.ny.gov/statistics/cancer/registry/appendix/neighborhoods.htm

`Zipcode` `Boro`

```{r, warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
zip <- read_csv('raw_data/demo_by_zip/nyc_zipcode.csv')
```

The Statistics of Income (SOI) Division’s ZIP code data is tabulated using individual income tax returns (Forms 1040) filed with the Internal Revenue Service (IRS) during the 12-month period, January 1, 2018 to December 31, 2018. 

`Total_income`

```{r, warning=FALSE, message=FALSE}
total_income <- read_csv('raw_data/demo_by_zip/tax_nation.csv') %>% select(Zipcode = ZIPCODE, Total_Income = A02650) 
total_income$Zipcode <- as.numeric(total_income$Zipcode)
nyc_zip_demo <- left_join(zip, total_income)
```

American Community Survey (ACS) provides characteristics at the zip code level (2006-2010).
https://www.psc.isr.umich.edu/dis/census/Features/tract2zip/

`Mean Income` `Median Income`

```{r, warning=FALSE, message=FALSE}
median_income <- read_csv('raw_data/demo_by_zip/income_nation.csv') %>% 
    select(Zipcode = Zip, 
           Median_Income = Median,
           Mean_Income = Mean,
           Population = Pop)
nyc_zip_demo <- left_join(nyc_zip_demo, median_income)
```

US Census Bureau provides demographic information (2010).

`population` `gender` `age`

```{r, warning=FALSE, message=FALSE}
population <- read_csv('raw_data/demo_by_zip/population_nation.csv')

nyc_zip_demo <- left_join(nyc_zip_demo, population)
```
